### 2021-01-13 paper/intro.tex
edits

>>>>

Our approach is only vaguely related to the theories of
\citet{DBLP:journals/cacm/Dijkstra75}, which provide an alternative
characterization of Hoare logic by mapping postconditions to preconditions
($\fwp$ and $\fwlp$) or preconditions to postconditions ($\fsp$).  Instead
our transformers $\aTr$ map preconditions to preconditions. The relation to
Hoare triples is that
\begin{align*}
  \hoare{\aForm}{\bCmd}{\bForm}
  \;\;\Leftrightarrow\;\;
  \hoare{\aTr(\aCmd,\aForm)}{\aCmd\SEMI\bCmd}{\bForm}
  .
\end{align*}
For example
\begin{gather*}
  \hoare{r{=}1}{\PW{y}{r}}{y{=}1}
  \\
  \hoare{x{=}1}{\PR{x}{r}\SEMI\PW{y}{r}}{y{=}1}
\end{gather*}

\endinput
